Untitled

### 2025-03-19 script/r/rbci_data.Rmd
maj rsf_index

countries <- unique(data_final$iso)

qog%<>%
  mutate(round=case_when(between(year, 2011, 2013)~5,
                         between(year, 2014, 2015)~6,
                         between(year, 2016, 2018)~7,
                         between(year, 2019, 2021)~8,
         TRUE~NA_integer_))

qog%<>%
  group_by(iso, round)%>%
  mutate(poly_mean = ifelse(is.na(round), NA_integer_, mean(vdem_polyarchy, na.rm = TRUE))) %>%
  mutate(med_corr_mean = ifelse(is.na(round), NA_integer_, mean(vdem_med_corrupt, na.rm = TRUE))) %>%
  ungroup()

qog %<>%
  filter(!is.na(round)) %>%
  distinct(iso, round, .keep_all = TRUE) %>%
  select(iso, round, poly_mean, med_corr_mean)

@@

vdem$v2med

@@

vdem%<>%
  select(iso, round, v2xedvd_inpt_mean2, v2x_polyarchy_mean2, v2xedvd_me_cent_mean2, v2medstateprint_mean2, v2medstatebroad_mean2, v2medpolstate_mean2, v2medpolnonstate_mean2, e_v2x_freexp_altinf_3C_mean2, e_v2x_freexp_altinf_4C_mean2, e_v2x_freexp_altinf_5C_mean2, v2x_freexp_mean2, v2xme_altinf_mean2, e_polity2_mean2)%>%
    distinct(iso, round, .keep_all = TRUE)

>>>>

countries <- data_final %>% filter(spl==1) %>% pull(iso) %>% unique()

qog %<>%
  select(
    year,
    ccodealp,
    aii_q55,
    aii_q56,
    fhp_mcpp5,
    vdem_mecorrpt,
    vdem_polyarchy,
    rsf_pfi1321,
    rsf_pfi0212,
    rsf_pfi,
    rsf_pci
  ) %>%
  rename(
    iso = ccodealp,
    fh_med_index = fhp_mcpp5,
    med_self_censor = aii_q55,
    citiz_self_censor = aii_q56,
    vdem_med_corrupt = vdem_mecorrpt,
    rsf_index = rsf_pfi1321
  )

qog %<>%
  mutate(round = case_when(
    year == 2013 ~ 5,
    between(year, 2014, 2015) ~ 6,
    between(year, 2016, 2018) ~ 7,
    between(year, 2019, 2021) ~ 8,
    TRUE ~ NA_integer_
  ))

qog %<>%
  group_by(iso, round) %>%
  mutate(poly_mean = ifelse(is.na(vdem_polyarchy), NA_integer_, mean(vdem_polyarchy, na.rm = TRUE))) %>%
  mutate(med_corr_mean = ifelse(is.na(vdem_med_corrupt), NA_integer_, mean(vdem_med_corrupt, na.rm = TRUE))) %>%
  mutate(rsf_index_mean = ifelse(is.na(rsf_index), NA_integer_, mean(rsf_index, na.rm = TRUE))) %>%
  ungroup()

qog %<>%
  filter(!is.na(round)) %>%
  distinct(iso, round, .keep_all = TRUE) %>%
  filter(iso %in% countries)%>%
  mutate(rsf_index_med_all=ifelse(is.na(round), NA_integer_, median(rsf_index_mean, na.rm=TRUE)))

qog %<>%
  select(iso,
         round,
         poly_mean,
         med_corr_mean,
         rsf_index_mean,
         rsf_index_med_all)

@@

@@

vdem%<>%
  mutate(e_polity2_med_all=ifelse(is.na(round), NA_integer_, median(e_polity2, na.rm=TRUE)))

vdem%<>%
  select(iso, round, v2xedvd_inpt_mean2, v2x_polyarchy_mean2, v2xedvd_me_cent_mean2, v2medstateprint_mean2, v2medstatebroad_mean2, v2medpolstate_mean2, v2medpolnonstate_mean2, e_v2x_freexp_altinf_3C_mean2, e_v2x_freexp_altinf_4C_mean2, e_v2x_freexp_altinf_5C_mean2, v2x_freexp_mean2, v2xme_altinf_mean2, e_polity2_mean2, e_polity2_med_all)%>%
    distinct(iso, round, .keep_all = TRUE)
